%==============================================================================
\chapter{Introduction}
\label{sec:intro}
%==============================================================================

For the last two decades, the $\Lambda$CDM model has been the standard model of cosmology. With only a few free parameters, it is able to explain a huge variety of observations; the existence and fluctuations of the Cosmic Microwave Background (CMB), the large scale structure in the Universe, the luminosity of supernovae of type Ia and the abundances of light elements all yield roughly consistent results for the standard model. Apart from the nature of Dark Matter and Dark Energy, the challenges for modern cosmology are the precise determination of the free parameters as well as the search for possible extensions to the standard model.

One tool to probe the $\Lambda$CDM Model and determine its parameters was provided by the discovery of cosmic shear: The distortion of light bundles travelling from distant galaxies through the matter distribution of the Universe to Earth provides useful insights on the large scale structure. Contrary to the analysis of the CMB by \citet{2018arXiv180706209P}, cosmic shear is more sensitive to the properties of the local Universe and thus provides an excellent consistency check for the standard model of cosmology. Current cosmic shear surveys are especially sensitive to the parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3}$, where $\sigma_8$ denotes the normalisation of the matter power spectrum and $\Omega_{\rm m}$ is the matter density.
It is interesting to note that all three current major cosmic shear results report a lower $S_8$ than inferred from CMB analysis: While \citet{2018arXiv180706209P} determined a value of $S_8 = 0.830 \pm 0.013$, 
%\citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data,
\citet{2018arXiv180909148H} report $S_8 = 0.800^{+0.029}_{-0.028}$ from analysis of the Subaru Hyper Suprime-Cam survey, \citet{2018arXiv181206076H} report $0.737_{-0.036}^{+0.040}$ from KiDS+VIKING data and the Dark Energy Survey \citep{2018PhRvD..98d3528T} reports $S_8=0.782\pm 0.027$. Also, \citet{2013MNRAS.432.2433H} report $S_8 = 0.759 \pm 0.020$ from analysis of CFHTLens data. This discrepancy has received a lot of attention \citep{2013PDU.....2..166V}. It could be interpreted as a statistical coincidence, a sign of new physics like massive neutrinos \citep{2014PhRvL.112e1303B}, time-varying dark energy or modified gravity \citep{2016A&A...594A..14P}; or as the manifestation of a systematic effect, either in the cosmic shear surveys or in the Planck mission \citep{2016ApJ...818..132A}, that is not yet accounted for. 

As weak gravitational lensing measures a tiny signal over a large sample, it is extremely sensitive to anything that systematically biases the measurements, such that the error bars in current surveys arise to equal parts from statistical and systematic uncertainties \citep[compare][]{2017MNRAS.465.1454H}. With next-generation surveys like the Large Synoptic Survey Telescope and Euclid right at the doorstep, systematic effects in gravitational lensing have received an unprecedented amount of attention \citep{2018arXiv181002353A,2019arXiv190207439B,2019arXiv190109488S}. %\todo{Citations.. \citet{2017MNRAS.464.1676A} has a few...}

To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}. To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics. As \citet{2017MNRAS.465.1454H} reported the significant detection of B-modes, it was well motivated to check for possible systematics that are not yet accounted for. Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.

One systematic effect is the variation of depth in a survey. While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions, that are found in ground-based surveys. To first order, this variation can be modelled by a step-like depth function which varies from pointing to pointing. In this work we assume the specifications of the Kilo-Degree Survey, namely a collection of $1\,\text{deg}^2$ square fields. 

We will give a brief overview over the necessary knowledge in cosmology and gravitational lensing in Chapter \ref{sec:theory}. We will then review the extent of the variation of depth in the KiDS+VIKING-450 survey in Chapter \ref{sec:eff_of_var_depth} and develop several models to describe its effect in Sections \ref{sec:toy_model} and \ref{sec:xipm_semianalytic}. Afterwards we will present our results in Chapter \ref{sec:results} and discuss them in Chapter \ref{sec:discussion}, focussing on the used simplifications and possible mitigation strategies.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End: 
